\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
      {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeProjectItem}[2]{
    \vspace{-1pt}\item
        \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
            \textbf{#1} \\
            \textit{\small#2} \\
        \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{description}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{description}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{\href{https://github.com/knotgud/}{\LARGE Daniel Lee}}
    & \href{mailto:daniel@devshell.net}{daniel@devshell.net}\\
    & (360)-909-6604\\
    & Camas, WA\\
\end{tabular*}


%--------SKILLS------------
\section{Skills}
\resumeSubHeadingListStart
    \resumeSubItem
    {\textbf{Languages}}
    {(\emph{Proficient}) Python, Golang, (\emph{Familiar}) C\#, C/x86 Assembly, SQL, Javascript, HTML/CSS}
    \resumeSubItem
    {\textbf{Technologies}}
    {Flask, Git, Docker Swarm, .NET Core, MySQL, Redis, Kafka, LaTeX, Bash, Vim}
\resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
\resumeSubHeadingListStart
    \resumeSubheading
    {OfficeAlly}{Vancouver, WA}
    {Web Developer}{May 2017 - Present}
        \resumeItemListStart
            \resumeItem
            {Developed applications and services to build and deploy on docker swarm.}
            \resumeItem
            {Refactored sections to improve overall code health and increase performance.}
            \resumeItem
            {Collaborated with developers to create optimal designs and workflows for back-end services.}
            \resumeItem
            {Reviewed colleague's code and change lists ensuring code quality and best practices}
            \resumeItem
            {Implemented agile and scrum methodology to improve velocity and increase team communication.}
            \resumeItem
            {Added comprehensive unit tests and practiced TDD to ensure code stability and reliability.}
            \resumeItem
            {Introduced gRPC and the micro-service architecture to support communication between different languages and environments across the company's applications and services.}
            \resumeItem
            {Added a caching mechanism to a taxing API route which improved performance of dependent services.}
            \resumeItem
            {Supported the adoption of Git from SVN by suggesting a series of workflows to ease transition.}
            \resumeItem
            {Contributed to discussions and documentation to improve and standardize company git practices such as branch naming, commit message formatting, and re-basing history.}
            \resumeItem
            {Discovered and reported critical security vulnerabilities that could cause massive damage to company systems and infrastructure.}
      \resumeItemListEnd
\resumeSubHeadingListEnd


%-----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart
    \resumeSubheading
    {Washington State University Vancouver}{Vancouver, WA}
    {Bachelor of Science in Computer Science}{Expected: May 2021}
\resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
\resumeSubHeadingListStart
    \resumeSubheading
    {Patient Visualization Tool} {Fall 2019}
    {A map based web app that assists in the discovery of healthcare providers} {}
    \resumeItemListStart
        \resumeItem
        {Demonstrated to a select group of corporate entities operating in pharmaceuticals and case management.}
        \resumeItem
        {Vuejs front-end using leaflet for mapping and material design components.}
        \resumeItem
        {Golang back-end gRPC service that aggregates data and serves summaries.}
    \resumeItemListEnd
    \resumeSubheading
    {Distributed Management Tool} {Spring 2019}
    {This software allows users to experiment with concurrent programming and distributed service design.} {}
    \resumeItemListStart
        \resumeItem
        {Application Stack: Command and Control (C2) server, Package download server, Advanced Persistent Threat (APT) application.}
        \resumeItem
        {APT has a tiny footprint and runs management functionality modularly upon requests.}
        \resumeItem
        {APT establishes a communication channel with the C2 and intelligently requests executables from local download servers.}
        \resumeItem
        {System is also capable of switching to a decentralized C2 system that uses the APTs and a version of the RAFT consensus algorithm.}
    \resumeItemListEnd
    \resumeSubheading
    {Systems Research and Applications (SRA) CubeSat Internals} {Fall 2018}
    {A distributed software that manages physical components of a Cube Satellite} {}
    \resumeItemListStart
        \resumeItem
        {Used in an annual competition hosted by the Experimental Sounding Rocket Association, this software provided communication to the satellite from a ground-station.}
        \resumeItem
        {Written in Go, these programs managed physical components of the 3u sized experimental cube satellite through a distributed platform across multiple microcomputers.}
        \resumeItem
        {Communication to the software controller was sent from the ground-station was sent via radio.}
    \resumeItemListEnd
\resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
